Optimized genome sequencing: onderzoeksprobleem

### 2015-02-19 probleemstelling/NoSQL_table.tex
probleemstelling

\multicolumn{1}{|l|}{\textbf{Indexing}}                  & Primary \& secondary on every attribute, B-tree    & Primary \& secondary, B-tree  & Primary \& secondary, LSM-tree                                                                                           & Primary \& secondary, LSM-tree                                                                                                         & Primary \& secondary{[}3{]}      & Primary \& secondary. Hash- \& tree-indexes                             \\ \midrule

>>>>

\multicolumn{1}{|l|}{\textbf{Indexing}}                  & Primary \& secondary on every attribute, B-tree    & Primary \& secondary, B-tree  & Primary \& secondary, LSM-tree                                                                                           & Primary \& secondary, LSM-tree                                                                                                         & Primary \& secondary      & Primary \& secondary. Hash- \& tree-indexes                             \\ \midrule
